### 2014-01-16 Draft/abstract.tex
added new version

\begin{abstract}

Recently many popular websites such as Twitter and Flickr expose their data through web service APIs, enabling third-party 
organizations to develop client applications that provide functionalities beyond what the original websites offer. These client applications should follow certain constraints in order to correctly interact with the web services.
Violations of such constraints can cause fatal errors 
or incorrect results in the client applications. However, these constraints are often not formally specified and thus not available for 
automatic verification of client applications. To address this issue, 
we propose a novel approach, called \tool,
%to automatically 
%infer dependency constraints on parameters for web services, via a 
%hybrid analysis of heterogeneous web service artifacts, including 
%the service documentation, the service SDKs, and the web services themselves. To evaluate our approach, we applied INDICATOR to infer dependency constraints for four popular web services. 
%The results showed that INDICATOR effectively infers constraints 
%with an average precision of 94.4\% and recall of 95.5\%.

>>>>

\begin{abstract}
Formal specifications of an Application Programming Interface (API) usage are highly desirable,
because they are the precursor to the formal analysis tools such as model checkers and runtime verifiers.
However, most API's do not have formal specifications.
In contrast documentation of methods contain detailed specifications of the usage in natural language text.
However, formal analysis tools are not designed to work on specifications in natural languages.
Manually writing formal specifications based on natural language text in API documents can be prohibitively time consuming and error prone.
To address this issue, we propose a natural language processing based novel approach \tool\ to precisely infer constraints from natural language text of API documents.
In particular, we focus on temporal constraints, that are defined as constraints on the
\textit{allowed sequence of invocations of methods within an API}.
To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
Our evaluation results show that \tool\ achieves an average of PP\% precision and RR\% recall
in inferring TT temporal constraints from more than ZZZZ sentences of API sentences.

%IS the approach automated
%precursor too strong word
% need to explain why moving from formal specifications to temporal constraints

% Goal statement
% The goal of this research is to facilitate the correct usage API methods by identifying temporal constraints etc..
% Is the approach automated ? Make a line about how you gonna
% conclusion of numbers 
% make it consistent APi documents, descriptions and sentences

### 2014-01-16 Draft/approach.tex
added new version

We next present our framework for inferring specifications from the method descriptions in API Documents. Figure~\ref{fig:approachOverview} gives an overview of our framework. Our framework consists of four major components: a parser, a preprocessor, an text-analysis engine, and a postprocessor.

The parser accepts online API description and parser them into an intermediate representation. The pre-processor accepts method descriptions and preprocesses the sentences in the descriptions, such as annotating sentence boundaries and reducing lexical tokens. 
The text-analysis engine accepts the pre-processed sentences and parses them using an NLP parser. The text-analysis engine further transforms the parsed sentences into the first-order-logic (FOL) representation and then leverages the FOL representation of a sentence to infer specifications. Finally, the postprocessor undoes any modifications done by the preprocessor to get refined specifications.

@@

\subsection{Parser}
\label{sub:parser}

Our parser accepts the online API documents and parses them into predefined categories. In particular, our parser extracts the following contents: 1) Summary of the API method, 2)Summary of request elements of the method, and 3) Summary of response elements of the method inclusive of error responses.

This step is required to extract the desired descriptive text from the various presentation styles of the API documents. In particular, deferential API documents may have styles of presenting information to developers inclusive of different levels of details, we chose very generic fields that are found across all documents.

Currently our prototype implementation extracts this information from \amazon. However almost all of the REST API developer documents are provided on-line as structured webpages, thus the parser can be easily extended to extract desired information from any REST API developer documents in general.

@@

The preprocessor accepts method application descriptions extracted by the parser and preprocesses the natural language text, to be further analyzed by the text-analysis engine. In particular, the preprocessor annotates special words and reduces the number of lexical tokens using semantic information. The preprocessing steps are required to increase the accuracy of the subsequent phases of \tool\ framework, described in detail in Section~\ref{sub:TAE}. We next describe in detail the preprocessing steps:

\textbf{1. Special word annotation}.
Since the exiting NLP techniques rely on accurate annotation of POS tags in a sentence, the accuracy of \tool\ to infer constraints is dependent on the accurate annotation of POS tags. While existing techniques work well on general linguistics, that does not necessary entail that they work well with domain specific text as well. In particular, with respect to API documents certain words have a very different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

Consider the word ``POST'' for instance. The online Oxford dictionary~\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word ``POST'', and none of them describes POST as a HTTP method supported by REST API meaning: \textit{``Creates a new entry in the collection. The new entry's URI is assigned automatically and is usually returned by the operation''}. Thus existing NLP techniques fail to accurately annotate the POS tags of the sentences involving word ``POST''.

This preprocessing step identifies such words from the sentences based on a domain-specific dictionary, and annotates them appropriately. This special annotation forces the underlying POS tagger to accurately annotate the POS tags of the words involving domain specific keywords.

From implementations perspective, we manually built the domain-specific dictionary using the glossary of terms collected from the web pertaining to REST API. We further leveraged the HTML style information in \amazon\ to look for words that were highlighted in code like format.

\textbf{2. Lexical tokens reduction}.

The reduction of lexical tokens greatly increases the accuracy of the analysis in the subsequent components of our framework. In particular, the preprocessor reduces lexical tokens by performing following subtasks

\textbf{1. Period Handling}. Besides marking the end of a sentence in simplistic English, the character period (`.') has other legal usages as well such as decimal representation (periods between numbers). Although legal, such usage hinder detection of sentence boundaries, thus forcing the subsequent components to return incorrect or imprecise results. We pre-process the sentences by annotating these usages for accurate detection of sentence boundaries. We achieve so by looking up known shorthand words from WordNet~\cite{wordnet} and detecting decimals, which are also the period character, by using regular expressions. From an implementation perspective, we have maintained a static lookup table of shorthand words observed in WordNet.

\textbf{2. Named Entity Handling}. Sometimes a sequence of words correspond to the name of entities that have a specific meaning collectively. For instance, consider the phrases \textit{``Amazon S3'', ``Amazon simple storage service''}, which are the names of the service. Further resolution of these phrases using grammatical syntax is unnecessary and would not bring forth any semantic value. Also these phrases contribute to length of a sentence that in turn negatively affects the accuracy of POS tagger. Thus, we identify such phrases and annotate them as single lexical units. We achieve so by maintaining a static lookup table.

\textbf{3. Abbreviation Handling}. Natural-language sentences often consist of abbreviations mixed with text. This can result in subsequent components to incorrectly parse a sentence. We find such instances and annotate them as a single entity. For example, text followed by abbreviations such as \textit{``Access Control Lists (ACL)''} is treated as single lexical unit. Detecting such abbreviations is achieved by using the common structure of abbreviations and encoding such structures into regular expressions. Typically, regular expressions provide a reasonable approximation for handling abbreviations.

\textbf{4. Frequent Phrases} Although the previous steps assist in bringing down the number of lexical tokens in a sentence, some sentences may still contain a considerable number of lexical tokens to overwhelm the underlying POS tagger. To address this issue we propose to further reduce the number of lexical tokens in a sentence  by annotating frequent phrases as a single lexical unit.

In particular, we use n-gram based approach as means to achieve this reduction. In the fields of computational linguistics and probability, an n-gram is a contiguous sequence of n words from a given sequence of text or speech. We first calculate the most frequently occurring n-grams in the text body. In particular, we are interested in the n-grams of length 4 or greater to achieve a reasonable reduction. We then prune the list of n-grams based on a subsumption. We consider a n-gram of length k ($n_k$) to subsume n-gram of length k-1 ($n_{k-1}$) iff $n_{k-1}$ is a substring of ($n_k$) and the frequency of occurrence of $n_{k-1}$ equals frequency of occurrence of $n_{k}$ . Finally, we rank the list of n-grams based on the frequency of their occurrence in the text, and select top-k n-grams for reduction.

@@

Although a POS tagger can be retrained to achieve these pre-processing steps, we prefer annotations to make our approach independent of any specific NLP infrastructure, thus ensuring interoperability with various POS taggers.

@@

The NLP parser accepts the pre-processed documents and annotates every sentence within each document using standard NLP techniques. From an implementation perspective, we chose the Stanford Parser~\cite{SNLP}. However, this component can be implemented using any other existing NLP libraries or frameworks. In particular, we annotate each sentence with POS annotations, Named-Entity Annotations and Stanford-Typed Dependencies. For more details on these tehniques and their application, please refer to ~\cite{Marneffe06LREC,Marneffe08COLING,pandita12:inferring, pandita13:WHYPER}.

%\begin{figure}
%	\centering
%%		\includegraphics[scale=0.6]{stanfordAnnotated.eps}
%	\caption{Sentence annotated with Stanford dependencies}
%	\label{fig:standep}
%\end{figure}
%
%Next we use an example to illustrate the annotations added by the NLP Parser. Consider the example sentence \textbf{\textit{``Also you can share the yoga exercise to your friends via Email and SMS.''}}, that indirectly refers to the READ\_CONTACTS permission. Figure~\ref{fig:standep} shows the sentence annotated with Stanford-typed dependencies. The words in red are the names of dependencies connecting the actual words of the sentence (in black). Each word is followed by the Part-Of-Speech (POS) tag of the word (in green). For more details on Stanford-typed dependencies and POS tags, please refer to ~\cite{Marneffe06LREC,Marneffe08COLING}.

@@

The text analysis engine component accepts the annotated documents and creates an intermediate representation of each sentence. We define our representation as a tree structure that is essentially a First-Order-Logic (FOL) expression. Research literature provides evidence of the the adequacy of using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring, pandita13:WHYPER}.

@@

In particular, the process of generation of intermediate-representation is an extension of the intermediate-representation generator component of \emph{WHYPER}~\cite{pandita13:WHYPER} with additional steps. In \emph{WHYPER}, the intermediate representation is generated based on principle of shallow parsing~\cite{Branimir2000}. They implemented their parser as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,SNLP,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.

However, we observed that intermediate-representation generator component of \emph{WHYPER}~\cite{pandita13:WHYPER} is overwhelmed by wordy sentences.This limitation mandates the use of additional novel technique of \textit{`Frequent Phrases Reduction'} in preprocessing phase. We further improve the accuracy of  parser by adopting a hybrid (leveraging both POS tags as well as Stanford-typed dependencies) approach.

Our implementation of shallow parser is a two phase process:

\begin{enumerate}
	\item{\textbf{POS Tags}}: We first parse a sentence based on the function of POS tags. In particular, we use semantic templates to logically break a sentences into smaller constituent sentences. For instance, consider the sentence \scriptsize``All objects (including all object versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted.''. \normalsize The Stanford parser inaccurately annotates the Stanford-typed dependencies of the sentence because of presence of different clauses acting on different subject-object pairs. We thus break down the sentence into two smaller tractable sentences:

	 \scriptsize All objects in the bucket must be deleted before the bucket itself can be deleted.

	 All objects including all object versions and Delete Markers.\normalsize

	 Table~\ref{tab:semanticTemplates} shows a list the semantic templates. Column ``Template'' describes conditions where the template is applicable and Column ``Summary'' describes the action taken by our shallow parser when the template is applicable. All of these semantic templates are publicly available on our project website~\cite{projectweb}. With respect to the previous example the template no. 3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable. Thus our shallow parser breaks the sentence into two individual sentences.

	\item{\textbf{Stanford-typed Dependencies}}: This phase is equivalent to the intermediate-representation generator component of the \emph{WHYPER}~\cite{pandita13:WHYPER}.

\end{enumerate}

@@

@@

%\algsetup{indent=1em}
%\begin{algorithm}[t!]
%\begin{algorithmic}[1]
%\begin{scriptsize}
%\REQUIRE K\_Graph $g$, FOL\_rep $rep$, Boolean $recursion$ 
%\ENSURE Boolean $isPStmt$
%\STATE $Boolean\ isPStmt\ =\ false$
%\STATE $String\ r\_name\ =\ g.resource\_Name$
%\STATE $FOL\_rep\ r'\ =\ rep.findLeafContaining(r\_name)$
%\STATE $List\ actionList\ =\ g.actionList$
%\WHILE{$(r'.hasParent)$}
%	\IF{$actionList.contains(r'.parent.predicate)$}
%		\STATE $isPStmt\ =\ true$
%		\STATE $break$
%	\ELSE
%		\IF{$actionList.contains(r'.leftSibling.predicate)$}
%			\STATE $isPStmt\ =\ true$
%			\STATE $break$
%		\ENDIF
%	\ENDIF
%	\STATE $r'\ =\ r'.parent$
%\ENDWHILE
%\IF{$((NOT(isPStmt))\ AND\ recursion)$}
%	\STATE $List\ resourceList\ =\ g.resourceList$
%	\FORALL{$(Resource\ res\ in\ resourceList)$}
%		\STATE $isPStmt\ =\ Sentence\_Annotator(getKGraph(res),\ rep,\ false)$
%		\IF{$isPStmt$}
%			\STATE $break$
%		\ENDIF
%	\ENDFOR
%\ENDIF
%\RETURN $isPStmt$
%\end{scriptsize}
%\end{algorithmic}
%\caption{Sentence\_Annotator}
%\label{alg:SenAnnotaator}
%\end{algorithm} 
%\begin{figure}
%	\centering
%%		\includegraphics[scale=0.4]{knowledge.eps}
%	\caption{Semantic Graph for the READ\_CONTACT permission}
%	\label{fig:knowledge}
%\end{figure} 

>>>>

We next present our framework for inferring specifications from the method descriptions in API Documents.
Figure~\ref{fig:approachOverview} gives an overview of our framework.
Our framework consists of four major components: an API parser, a preprocessor, a text-analysis engine, and a postprocessor.

The API parser accepts online API description and extracts method descriptions.
The pre-processor accepts method descriptions and preprocesses the sentences in the descriptions, such as annotating sentence boundaries and reducing lexical tokens. 
The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation and then leverages the FOL representation of a sentence to infer specifications.
Finally, the postprocessor undoes any modifications done by the preprocessor to get refined specifications.

@@

\subsection{API Parser}
\label{sub:parser}

Our API parser accepts the online API documents and extracts method descriptions from it.
In particular, our parser extracts the following fields within method descriptions: 
1) \textit{Summary of the API method},
2) \textit{Summary of request elements of the API method}, and 
3) \textit{Summary of response elements of the method (inclusive of error responses)}.

This step is required to extract the desired descriptive text from the various presentation styles of the API documents.
In particular, different API documents may have different styles of presenting information to developers.
This difference in style may include the difference in the level of detail presented to the developer.
We thus chose very only generic fields that are essential to API methods.

Currently our prototype implementation extracts this information from online \amazon\ only. 
However, almost all of the REST API developer documents are provided online as structured webpages.
Thus, current implementation of parser can be easily extended to extract desired information from any REST API developer documents.

@@

The preprocessor accepts API method descriptions extracted by the parser and preprocesses the natural language text, to be further analyzed by the text-analysis engine.
The preprocessing steps are required to increase the accuracy core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ framework.
In particular, the preprocessor first employs the noun boosting followed by heuristics listed under lexical token reduction, as introduced in Section~\ref{sub:SENLPback}.

From an implementation perspective, we manually built the domain dictionaries for the preprocessing using the glossary of terms collected from the websites pertaining to REST API.
We further leveraged the HTML style information in \amazon\ to look for words that were highlighted in code like format. We further leveraged WordNet to maintain a static lookup table of shorthand words to aid named entity handling and abbreviation handling.

Although the previous techniques and heuristics significantly lower the number of lexical tokens in a sentence, some sentences may still contain a considerable number of lexical tokens to overwhelm the POS tagger.
To address this issue, we propose a novel technique (\textit{`Frequent Phrases Reduction'}) to further reduce the number of lexical tokens in a sentence by annotating frequent phrases as a single lexical unit.

In particular, we use n-gram based approach as means to achieve this reduction. 
In the fields of computational linguistics and probability, an n-gram is a contiguous sequence of n words from a given sequence of text or speech. 
We first calculate the most frequently occurring n-grams in the text body. 
In particular, we are interested in the n-grams of length 4 or greater to achieve a reasonable reduction. 
We then prune the list of n-grams based on a subsumption. 
We consider a n-gram of length k ($n_k$) to subsume n-gram of length k-1 ($n_{k-1}$) iff $n_{k-1}$ is a substring of ($n_k$) and the frequency of occurrence of $n_{k-1}$ equals frequency of occurrence of $n_{k}$.
Finally, we rank the list of n-grams based on the frequency of their occurrence in the text, and select top-k n-grams for reduction.

@@

%Although a POS tagger can be retrained to achieve these pre-processing steps, we prefer annotations to make our approach independent of any specific NLP infrastructure, thus ensuring interoperability with various POS taggers.

@@

The NLP parser accepts the pre-processed documents and annotates every sentence within each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
From an implementation perspective, we chose the Stanford parser~\cite{SNLP}.
However, this component can be implemented using any other existing NLP libraries or frameworks.
In particular, we annotate each sentence with POS tags, named-entity Annotations and Stanford-typed dependencies.
For more details on these techniques and their application, please refer to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.

%\begin{figure}
%	\centering
%%		\includegraphics[scale=0.6]{StanfordAnnotated.eps}
%	\caption{Sentence annotated with Stanford dependencies}
%	\label{fig:standep}
%\end{figure}
%
%Next we use an example to illustrate the annotations added by the NLP Parser. Consider the example sentence \textbf{\textit{``Also you can share the yoga exercise to your friends via Email and SMS.''}}, that indirectly refers to the READ\_CONTACTS permission. Figure~\ref{fig:standep} shows the sentence annotated with Stanford-typed dependencies. The words in red are the names of dependencies connecting the actual words of the sentence (in black). Each word is followed by the Part-Of-Speech (POS) tag of the word (in green). For more details on Stanford-typed dependencies and POS tags, please refer to ~\cite{Marneffe06LREC,Marneffe08COLING}.

@@

The text analysis engine component accepts the annotated documents and creates an intermediate representation of each sentence.
We define our representation as a tree structure that is essentially a First-Order-Logic (FOL) expression.
Research literature provides evidence of the adequacy of using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring, pandita13:WHYPER}.

@@

As described in Section~\ref{sub:SENLPback} the intermediate representation generation technique is based on the principle of shallow parsing~\cite{Branimir2000}. 
In particular, the intermediate-representation technique is implemented as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,SNLP,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.

However, we observed that such implementation is overwhelmed by complex sentences.
This limitation mandates the use of additional novel technique of \textit{`Frequent Phrases Reduction'} in preprocessing phase.
We further improve the accuracy of intermediate-representation generation by proposing an hybrid approach, i.e. taking into consideration both the POS tags as well as Stanford-typed dependencies.
The POS tags which annotate the syntactical structure of a sentence are used to further simplify the constituent elements in a sentence. 
We then use the Stanford-typed dependencies that annotate the grammatical relationships between words to construct our FOL representation.
Thus, the intermediate representation generator used in this work is two phase process as opposed to previous work~\cite{pandita12:inferring, pandita13:WHYPER}. 
We next describe these two phases:

\textbf{POS Tags}: We first parse a sentence based on the function of POS tags. 
In particular, we use semantic templates to logically break a sentences into smaller constituent sentences. 
For instance, consider the sentence:

\begin{center}
\scriptsize``All objects (including all object versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted.''. \normalsize
\end{center}

The Stanford parser inaccurately annotates the Stanford-typed dependencies of the sentence because of presence of different clauses acting on different subject-object pairs.
We thus break down the sentence into two smaller tractable sentences:

\begin{center}
\scriptsize \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted.}''

\textit{``All objects including all object versions and Delete Markers.''}\normalsize 
\end{center}

Table~\ref{tab:semanticTemplates} shows a list the semantic templates used in this phase.
Column ``Template'' describes conditions where the template is applicable and Column ``Summary'' describes the action taken by our shallow parser when the template is applicable.
All of these semantic templates are publicly available on our project website~\cite{projectweb}.
With respect to the previous example the template no. 3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
Thus our shallow parser breaks the sentence into two individual sentences.

\textbf{Stanford-typed Dependencies}: This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}.

\subsection{Specification Extractor}
\label{sub:SE}

This component accepts the FOL representation of the sentence.

\begin{itemize}
\item Extracts Specifications from FOL representation. 
\item Specifically looking for modal modifies ``can, could, may, must, should'' 
\item Takes into consideration the negative quantifiers.
\item Algorithm to infer the sequence of operations.
\end{itemize}

\subsection{Postprocessor}
\label{sub:postpro}
undoing pre-processing and Hybrid intermediate representation generation.

@@

\subsection{Semantic-Graph Generator}
\label{sub:ACA}

A key way of identifying reference to a method within the API in our proposed framework is the employment of a semantic graph of an API.
In particular, we propose to initially infer such graphs from API documents.
Manually creating a semantic graph is prohibitively time consuming and may be error prone.
We thus employ a systematic methodology (proposed previously in ~\cite{pandita13:WHYPER}) to infer such semantic graphs from API documents that can potentially be automated.
We first consider the name of the class.
We then find the synonyms terms used refer to the class in question.
The synonym terms are listed as by breaking down the camel-case notation in the class name.
This list is further augmented by listing the name of the parent classes and implemented interfaces if any.

\begin{figure}
	\centering
		\includegraphics[scale=0.4]{KnowledgeGraph.eps}
	\caption{Semantic Graph for the \CodeIn{BufferedInputStream} class in Java}
	\label{fig:knowledge}
\end{figure}

We then systematically inspect the member methods to identify actions applicable to the objects represented by the class. From the name of a public method (describing a possible action on the object), we extract verb phrases. The verb phrases are used as the associated actions applicable on the object. For instance, \CodeIn{BufferedInputReader} defines operations available, close, mark, and so on. We associate these operations with the objects of type \CodeIn{BufferedInputReader}. Figure~\ref{fig:knowledge} shows a sub-graph of  graph for \CodeIn{BufferedInputReader} class. The phrases in solid rectangles are synonyms of the class name \CodeIn{BufferedInputReader}. The phrases in rounded rectangle are the actions applicable on \CodeIn{BufferedInputReader} class.

\algsetup{indent=1em}
\begin{algorithm}[t!]
\begin{algorithmic}[1]
\begin{scriptsize}
\REQUIRE K\_Graph $g$, FOL\_rep $rep$ 
\ENSURE String $action$
\STATE $String\ action\ =\ \phi$
\STATE $List\ r\_name\_list\ =\ g.resource\_Names$
\STATE $FOL\_rep\ r'\ =\ rep.findLeafContaining(r\_nam\_list)$
\STATE $List\ actionList\ =\ g.actionList$
\WHILE{$(r'.hasParent)$}
	\IF{$actionList.contains(r'.parent.predicate)$}
		\STATE $action\ =\ actionList.matching(r'.parent.predicate)$
		\STATE $break$
	\ELSE
		\IF{$actionList.contains(r'.leftSibling.predicate)$}
			\STATE $action\ =\ actionList.matching(r'.leftSibling.predicate)$
			\STATE $break$
		\ENDIF
	\ENDIF
	\STATE $r'\ =\ r'.parent$
\ENDWHILE
\RETURN $action$
\end{scriptsize}
\end{algorithmic}
\caption{Action\_Extractor}
\label{alg:SenAnnotaator}
\end{algorithm}

\begin{algorithm}[t!]
\begin{algorithmic}[1]
\begin{scriptsize}
\REQUIRE List $methodList$ 
\ENSURE Graph $seq\_Graph$
\STATE $Graph\ seq\_Graph\ =\ \phi$
\STATE $Map\ idx\ = createIdx(methodList)$

\FORALL{$Method\ mtd\ in\ methodList$} 
	\STATE $seq\_Graph.addVertex(mtd)$
\ENDFOR

\FORALL{$Method\ mtd\ in\ methodList$} 
	\IF{$mtd.isPublic()$}
		\IF{$!mtd.isStatic()$}
			\STATE $List\ preList\ =\ idx.query(mtd.declaringType)$
			\FORALL{$Method\ mtd'\ in\ preList$}
				\STATE $seq\_Graph.addEdge(mtd',mtd)$
			\ENDFOR
		\ENDIF
		\FORALL{$Parameter\ param\ in\ mtd.getParameters()$}
			\IF{$!isBasicType(param.Type)$}
				\STATE $List\ preList\ =\ idx.query(paramType)$
				\FORALL{$Method\ mtd'\ in\ preList$}
					\STATE $seq\_Graph.addEdge(mtd',mtd)$
				\ENDFOR				
			\ENDIF
		\ENDFOR
	\ENDIF
\ENDFOR
\RETURN $seq\_Graph$
\end{scriptsize}
\end{algorithmic}
\caption{Type\_Sequence\_Builder}
\label{alg:SeqAnnotaator}
\end{algorithm}

@@

### 2014-01-16 Draft/background.tex
added new version

Although, well suited for human communication, converting natural language into unambiguous specifications that can be processed and understood by computers is very difficult.  Recently, a lot of exciting work has been carried out in the area of Natural Language Processing (NLP), with existing NLP techniques proving to be fairly accurate in highlighting grammatical structure of a natural language sentence. However, existing NLP techniques are still in the processing phase and not in understanding phase.  We briefly introduce the NLP techniques used in this work.

@@

\textbf{Phrase and clause parsing}. Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase). Chunking thus further enhances the syntax of a sentence on top of POS tagging. Current state-of-the-art approaches can achieve around 90\%~\cite{SNLP1} accuracy in classifying phrases and clauses over well written news articles.

@@

>>>>

Natural language is well suited for human communication, but converting natural language into unambiguous specifications that can be processed and understood by computers is difficult.
However, research advances~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03} have increased the accuracy of existing NLP techniques to annotate the grammatical structure of a sentence.
These advances in NLP have inspired researchers/practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt/apply NLP techniques to solve problems in software engineering domain.

In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
We next briefly introduce the techniques used in this work that have been grouped into broad categories.
We first introduce the core NLP techniques used in this work.
We then introduce the software engineering specific NLP techniques proposed in previous work~\cite{pandita12:inferring,pandita13:WHYPER} that have been used in this work.

\subsection{Core NLP techniques}
\label{sub:CoreNLPback}

%Recently, a lot of exciting work has been carried out in the area of Natural Language Processing (NLP), with existing NLP techniques proving to be fairly accurate in highlighting grammatical structure of a natural language sentence. However, existing NLP techniques are still in the processing phase and not in understanding phase.  We briefly introduce the NLP techniques used in this work.

@@

\textbf{Phrase and Clause Parsing}. Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase). Chunking thus further enhances the syntax of a sentence on top of POS tagging. Current state-of-the-art approaches can achieve around 90\%~\cite{SNLP1} accuracy in classifying phrases and clauses over well written news articles.

@@

\subsection{Software engineering specific NLP techniques}
\label{sub:SENLPback}

\textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However, as mentioned earlier, POS tagging work well on well written news articles which does not necessary entail that they work well with domain specific text as well.
Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
In particular, with respect to API documents certain words have a very different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

Consider the word \CodeIn{POST} for instance. 
The online Oxford dictionary~\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method
~\footnote{In HTTP vocabulary \CodeIn{POST} means: ''Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}
supported by REST API.
Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

Noun Boosting identifies such words from the sentences based on a domain-specific dictionaries, and annotates them appropriately.
The annotation assists the POS tagger to accurately annotate the POS tags of the words thus inturn increasing accuracy of advanced NLP techniques such as chunking and typed dependency annotation.

\textbf{Lexical Token Reduction}~\cite{pandita13:WHYPER}.
These are a group of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.
The accuracy of core NLP techniques is inversely proportional to the number of lexical tokens in a sentence.
Thus, the reduction in the number of lexical tokens greatly increases the accuracy of core NLP techniques. 
In particular, following heuristics have been used in previous work to achieve the desired reduction of lexical tokens:

\begin{itemize}

\item \textbf{Period Handling}. Besides marking the end of a sentence in simplistic English, the character period (`.') has other legal usages as well such as decimal representation (periods between numbers).
Although legal, such usage hinder detection of sentence boundaries, thus causing core NLP techniques to return incorrect or imprecise results.
The text is pre-processed by annotating these usages for accurate detection of sentence boundaries.

\item \textbf{Named Entity Handling}. Sometimes a sequence of words correspond to the name of entities that have a specific meaning collectively.
For instance, consider the phrases \textit{``Amazon S3'', ``Amazon simple storage service''}, which are the names of the service.
Further resolution of these phrases using grammatical syntax is unnecessary and would not bring forth any semantic value.
Also these phrases contribute to length of a sentence that in turn negatively affects the accuracy of core NLP techniques.
This heuristic annotates the phrase representing the name of the entities as a single lexical token.

\item \textbf{Abbreviation Handling}. Natural-language sentences often consist of abbreviations mixed with text.
This can result in subsequent components to incorrectly parse a sentence.
This heuristic finds such instances and annotates them as a single lexical unit.
For example, text followed by abbreviations such as \textit{``Access Control Lists (ACL)''} is treated as single lexical unit.
Detecting such abbreviations is achieved by using the common structure of abbreviations and encoding such structures into regular expressions.
Typically, regular expressions provide a reasonable approximation for handling abbreviations.

\end{itemize}

\textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}.
This technique accepts the syntax-annotated sentences and builds a First-Order-Logic(FOL) representation of the sentence.
Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
In particular, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator based on shallow parsing~\cite{Branimir2000} techniques. 
The shallow parser itself is implemented as sequence of cascading finite state machines based on the functions of stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.

In next section we describe our proposed generic approach to infer constraints from API documents.

### 2014-01-16 Draft/conclusion.tex
added new version

%API documents provide specification information about how to use a particular method within a class by means of method descriptions. However, specifications described in natural Language in API documents are not amenable to formal verification by existing verification tools.

%Specifications described in natural language in API documents are not amenable to formal verification by existing verification tools. In this paper, we have presented a novel approach for inferring formal specifications from API documents targeted towards code contract generation. Our evaluation results show that our approach has an average of 92\% precision and 93\% recall in identifying sentences describing code contracts from over 2500 sentences. Furthermore, our results also show that our approach has an average of 83.4\% accuracy in inferring specifications from sentences describing code contracts out of over 1600 sentences.

>>>>

Although highly desirable, most API's do not have formal specifications.
In contrast documentation of methods contain detailed specifications of the usage in natural language text.
However, formal analysis tools are not designed to work on specifications in natural languages.
Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
To address this issue, we proposed a novel approach \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
Our evaluation results show that \tool\ achieves an average of PP\% precision and RR\% recall
in inferring TT temporal constraints from more than ZZZZ sentences of API documents.
